---
title: "Stock_Sorting_With_R"
author: "Md. Shahadat Hossain"
date: "9/24/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Chepter_1

In this section, We will put the neccessary packages for importing fundamental data from various websites. 

```{r, include=FALSE}
# Quietly make sure all the required packages are installed
invisible(lapply(c('quantmod', 'dplyr', 'tidyquant','tidyverse'), function(pkg) {
  if (system.file(package = pkg) == '')
    install.packages(pkg)
}))
```

```{r,include=FALSE}
library(quantmod)
library(dplyr)
library(tidyquant)
library(tidyverse)
```

With the following code we will different indexes available in the market. 

```{r,include=FALSE}
tq_index_options()
```

From the above mentioned indices, We are only interested on S&P 500. 

```{r, include=TRUE}
SP500 <- tq_index("SP500")
head(SP500)
```

Lets see how many unique company, ticker and industry they have taken to construct this portfolio. 

```{r, include=TRUE}
SP500[,c(1,2,4)] %>% 
    lapply(function(x) x %>% unique() %>% length()) %>%
    unlist()
```

We can see that, they have used 505 seperate company with tickers and 11 sector. 

```{r, include=TRUE}
Indutry_Company<-SP500 %>%
    # Summarize data by frequency
    group_by(sector) %>%
    summarise(Count = n())
nrow(Indutry_Company)
```
So, we can see that they have used 11 industry for the constructing this portfolio.

```{r, include=TRUE}
# Visualize
Indutry_Company%>%
    ggplot(aes(x = sector %>% fct_reorder(count),
               y = count
               )) + 
    geom_bar(stat = "identity") +
    geom_text(aes(label = count), size = 3, nudge_y = 4, nudge_x = .1) + 
    scale_y_continuous(limits = c(0,100)) +
    ggtitle(label = "Sector Frequency Among SP500 Stocks") +
    xlab(label = "Sector") +
    theme(plot.title = element_text(size = 16)) + 
    coord_flip() 
```

Separating the distribution of securities into industry sectors shows us our options if we were to select stocks using a diversification strategy. It’s important to remember that a risk mitigation technique is to select a basket (or portfolio) of stocks that have low return correlation. Typically, selecting from different industries and sectors helps to reduce this correlation and diversify the portfolio. 

Lets start Stock analysis. For this section, I am going to use all stocks those have been used in SP500 Index

```{r, include=TRUE}
Stock_Selected<-SP500$symbol
```

```{r, include=TRUE, warning=FALSE}
start_date<-"2016-01-01"
end_date<-"2017-01-01"
mult_stocks <- tq_get(Stock_Selected,
                      get  = "stock.prices",
                      from = start_date,
                      to   = end_date)
```

```{r, include=TRUE}
length(levels(factor(mult_stocks$symbol)))
```

```{r, include=FALSE}
#mult_stocks <- mult_stocks %>%
  #select(date,symbol, Price=adjusted)
#colnames(mult_stocks) <- c("Date", "Symbol", "Price")
#head(mult_stocks)
```

```{r, include=TRUE}
mult_stocks <- mult_stocks[,c(1,2,8)]
colnames(mult_stocks) <- c("Symbol", "Date", "Price")
head(mult_stocks)
```

```{r, include=TRUE}
mult_stocks_Spread<-spread(mult_stocks, Symbol, Price)
head(mult_stocks_Spread)
```

We need to transform dataset format into xts. This will help us to calculate Returns.

```{r, include=TRUE}
mult_stocks_Spread.XTS<-xts(mult_stocks_Spread[,-1], order.by = mult_stocks_Spread$Date)
class(mult_stocks_Spread.XTS)
```

For calculating returns, we will use PerformanceAnalytics package. 

```{r, include=TRUE}
# install.packages("PerformanceAnalytics")
library(PerformanceAnalytics)
```

```{r, include=TRUE}
Logarithmic_Returns.XTS<-Return.calculate(mult_stocks_Spread.XTS, method = "log")
```



```{r, include=TRUE}
Logarithmic_Returns.XTS<-Logarithmic_Returns.XTS[-1,]
```

```{r, include=TRUE}
head(Logarithmic_Returns.XTS[,1:6])
```


```{r, include=TRUE}
Mean_Returns<-as.data.frame(lapply(Logarithmic_Returns.XTS,FUN = mean))
```

```{r, include=TRUE}
options(scipen = TRUE)
Mean_Returns<-gather(Mean_Returns)
colnames(Mean_Returns)<-c("Ticker", "Mean_Return")
head(Mean_Returns)
```



```{r, include=TRUE}
Return_Variance<-as.data.frame(lapply(Logarithmic_Returns.XTS,FUN = var))
```

```{r, include=TRUE}
Return_Variance<-gather(Return_Variance)
colnames(Return_Variance)<-c("Ticker", "Return_Variance")
head(Return_Variance)
```



```{r, include=TRUE}
Retrun_Statistics<-Mean_Returns%>%
  inner_join(Return_Variance, by = 'Ticker')
head(Retrun_Statistics)
```

```{r, include=TRUE}
Return_Standard_Deviation<-as.data.frame(lapply(Logarithmic_Returns.XTS,FUN = sd))
```


```{r, include=TRUE}
Return_Standard_Deviation<-gather(Return_Standard_Deviation)
colnames(Return_Standard_Deviation)<-c("Ticker", "Return_Standard_Deviation")
head(Return_Standard_Deviation)
```

```{r, include=TRUE}
Retrun_Statistics<-Retrun_Statistics%>%
  inner_join(Return_Standard_Deviation, by = 'Ticker')
head(Retrun_Statistics)
```



```{r, include=TRUE}
plot(Retrun_Statistics$Return_Standard_Deviation,Retrun_Statistics$Mean_Return, type = "p")
```

```{r, include=TRUE}
plot(Retrun_Statistics$Return_Variance,Retrun_Statistics$Mean_Return, type = "p")
```



```{r, include=TRUE}
Cumulative_Logarithmic_Returns.XTS<-cumsum(Logarithmic_Returns.XTS)
plot(Cumulative_Logarithmic_Returns.XTS)
```

```{r, include=TRUE}
N<-ncol(Logarithmic_Returns.XTS)
# Create the weights
eq_weights<-c(rep(1/N,N))
sum(eq_weights)
```

Creating a portfolio using the buy and hold strategy using Return.portfolio() . Note, you do not need to specify a rebalance period . Call this Port_Logarithmic_Return_BH .

```{r, include=TRUE}
# Create a portfolio using buy and hold
Port_Logarithmic_Return_BH<-Return.portfolio(R = Logarithmic_Returns.XTS, weights = eq_weights )
```

```{r, include=TRUE}
sapply(Logarithmic_Returns.XTS,function(x)sum(is.na (x)))
```