---
titlD: "Presentation_02"
author: "Md. Shahadat Hossain"
date: "2 October 2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
# Quietly make sure all the required packages are installed
invisible(lapply(c('quantmod', 'dplyr', 'tidyquant','tidyverse', 'XML', "rvest", "TTR"), function(pkg) {
  if (system.file(package = pkg) == '')
    install.packages(pkg)
}))
```

```{r,include=TRUE, warning=FALSE, message=FALSE}
library(quantmod)
library(dplyr)
library(tidyquant)
library(tidyverse)
library(XML)
library(rvest)
library(TTR)
```

From the above mentioned indices, We are only interested on S&P 500. 

```{r, include=TRUE}
SP500 <-read.csv("C:/Users/Md. Shahadat Hossain/Desktop/Portfolio_Management_2019/SP500.csv")
SP500<-SP500[,-1]
head(SP500)
```

```{r, include=TRUE}
SP500<-SP500%>%
  select(Ticker=Symbol, Company=Company)
SP500$Ticker<-as.character(SP500$Ticker)
head(SP500)
```

```{r, include=TRUE}
EPS_Stock_Ranking<-read.csv("C:/Users/Md. Shahadat Hossain/Desktop/Portfolio_Management_2019/EPS_Stock_Ranking.csv")
EPS_Stock_Ranking<-as.tibble(EPS_Stock_Ranking[,-1])
EPS_Stock_Ranking$Ticker<-as.character(EPS_Stock_Ranking$Ticker)
head(EPS_Stock_Ranking)
levels(factor(EPS_Stock_Ranking$Portfolio))
```

```{r, include=TRUE}
Stock_Selected<-SP500%>%
  inner_join(EPS_Stock_Ranking, by = "Ticker")
head(Stock_Selected)
write.csv(Stock_Selected, "C:/Users/Md. Shahadat Hossain/Desktop/Portfolio_Management_2019/Stock_Selected.csv")
```

```{r, include=TRUE}
Stocks_with_missing_beta<-which(is.na(Stock_Selected$Beta))
Stocks_with_missing_beta<-Stock_Selected[Stocks_with_missing_beta, ]
Stocks_with_missing_beta
```



```{r, include=TRUE}
Ticker<-c("GOOG", "AMCR", "CBOE", "CTVA", "DISCK", "DOW", "DD", "FOXA", "FOX", "LW", "LIN", "NWS", "FTI", "UA")
Beta_M<-c(0.94, 0.27, -0.02, NA, 1.38, NA, 1.24, NA, NA, 0.18, 0.48, 1.15, 1.66, 1.09)
Stocks_with_missing_beta_Fill<-as.data.frame(cbind(Ticker, Beta_M))
Stocks_with_missing_beta_Fill$Beta_M<-as.numeric(as.character(Stocks_with_missing_beta_Fill$Beta_M))
Stocks_with_missing_beta_Fill$Ticker<-as.character(Stocks_with_missing_beta_Fill$Ticker)
Stocks_with_missing_beta_Fill
```


```{r, include=TRUE}
Stocks_with_missing_beta<-Stocks_with_missing_beta%>%
  inner_join(Stocks_with_missing_beta_Fill, by="Ticker")%>%
  select(Ticker, Company, EPS_ttm, Beta_M)%>%
  mutate(Beta = Beta_M)%>%
  select(Ticker, Company, EPS_ttm, Beta)
Stocks_with_missing_beta
```

```{r, include=TRUE}
Stock_Selected<-na.omit(Stock_Selected)
Stock_Selected<-rbind(Stock_Selected, Stocks_with_missing_beta)
tail(Stock_Selected)
write.csv(Stock_Selected, "C:/Users/Md. Shahadat Hossain/Desktop/Portfolio_Management_2019/Stock_Selected.csv")
```

```{r, include=TRUE}
# Beta Distribution of S&P 500
x <- na.omit(Stock_Selected$Beta)
h<-hist(x, breaks=50, col="green", xlab="Beta",
        main="Beta Distribution of S&P 500 with Normal Curve")
xfit<-seq(min(x),max(x),length=40)
yfit<-dnorm(xfit,mean=mean(x),sd=sd(x))
yfit <- yfit*diff(h$mids[1:2])*length(x)
lines(xfit, yfit, col="blue", lwd=3)
```


```{r, include=TRUE}
Aggressive_Portfolio<-top_n(Stock_Selected, 20, Beta) 
Aggressive_Portfolio
```


```{r, include=TRUE}
Stock_Selected_Ticker<-Aggressive_Portfolio$Ticker
```

```{r, include=TRUE, warning=FALSE}
start_date<-"2014-08-31"
end_date<-"2019-08-31"
mult_stocks <- tq_get(Stock_Selected_Ticker,
                      get  = "stock.prices",
                      from = start_date,
                      to   = end_date)
```

```{r, include=TRUE}
length(levels(factor(mult_stocks$symbol)))
```


```{r, include=TRUE}
mult_stocks <- mult_stocks[,c(1,2,8)]
colnames(mult_stocks) <- c("Ticker", "Date", "Price")
head(mult_stocks)
```

```{r, include=TRUE}
mult_stocks_Spread<-spread(mult_stocks, Ticker, Price)
head(mult_stocks_Spread)
```

We have three stocks which have missing value. We want to exclude those stocks from 

```{r, include=TRUE}
# Finding those columns which have missing values
Missing_Values<-as.data.frame(sapply(mult_stocks_Spread[,-1], function(x) sum(is.na(x))))
colnames(Missing_Values)<-c( "No_Missing_Values")
# Now we need to convert row names into a column called Tickers
Missing_Values <- data.frame(Tickers = row.names(Missing_Values), Missing_Values)
# Getting ride of row names
rownames(Missing_Values) <- c()
# Now Checking which Rows have missing value.
which(Missing_Values$No_Missing_Values>0)
# Lets see which tickers have missing value.
# Missing_Values[c(195, 292, 446),]
Missing_Values[which(Missing_Values$No_Missing_Values>0),]
```

Now We want to exclude this three stocks from our stock returns.

```{r, include=TRUE}
# Picking those tickers which we want to exclude from out return dataset. 
drops <- Missing_Values[which(Missing_Values$No_Missing_Values>0),]$Tickers
mult_stocks_Spread<-mult_stocks_Spread[ , !(names(mult_stocks_Spread) %in% drops)]
```

We need to transform dataset format into xts. This will help us to calculate Returns.

```{r, include=TRUE}
mult_stocks_Spread.XTS<-xts(mult_stocks_Spread[,-1], order.by = mult_stocks_Spread$Date)
class(mult_stocks_Spread.XTS)
```

For calculating returns, we will use PerformanceAnalytics package. 

```{r, include=TRUE}
# install.packages("PerformanceAnalytics")
library(PerformanceAnalytics)
```

```{r, include=TRUE}
Logarithmic_Returns.XTS<-Return.calculate(mult_stocks_Spread.XTS, method = "log")
head(Logarithmic_Returns.XTS[,1:6])
```



```{r, include=TRUE}
tail(Logarithmic_Returns.XTS[,1:6])
```

```{r, include=TRUE}
Logarithmic_Returns.XTS<-Logarithmic_Returns.XTS[-1,]
head(Logarithmic_Returns.XTS[,1:6])
```


```{r, include=TRUE}
Aggressive_Portfolio_Stocks_Logarithmic_Returns.DF<-data.frame(Date=index(Logarithmic_Returns.XTS), coredata(Logarithmic_Returns.XTS))
head(Aggressive_Portfolio_Stocks_Logarithmic_Returns.DF[,1:6])
```

```{r, include=TRUE}
write.csv(Aggressive_Portfolio_Stocks_Logarithmic_Returns.DF,"C:/Users/Md. Shahadat Hossain/Desktop/Portfolio_Management_2019/Aggressive_Portfolio_Stocks_Logarithmic_Returns.csv")
```

```{r, include=TRUE}
Defensive_Portfolio<-Stock_Selected %>%
  filter(!is.na(Beta))%>%
  arrange(desc(Beta)) %>%
  slice((nrow(Stock_Selected)-23):nrow(Stock_Selected)) 
Defensive_Portfolio
```


```{r, include=TRUE}
Stock_Selected_Ticker<-Defensive_Portfolio$Ticker
```

```{r, include=TRUE, warning=FALSE}
start_date<-"2014-08-31"
end_date<-"2019-08-31"
mult_stocks <- tq_get(Stock_Selected_Ticker,
                      get  = "stock.prices",
                      from = start_date,
                      to   = end_date)
```

```{r, include=TRUE}
length(levels(factor(mult_stocks$symbol)))
```


```{r, include=TRUE}
mult_stocks <- mult_stocks[,c(1,2,8)]
colnames(mult_stocks) <- c("Ticker", "Date", "Price")
head(mult_stocks)
```

```{r, include=TRUE}
mult_stocks_Spread<-spread(mult_stocks, Ticker, Price)
head(mult_stocks_Spread)
```

We have three stocks which have missing value. We want to exclude those stocks from 

```{r, include=TRUE}
# Finding those columns which have missing values
Missing_Values<-as.data.frame(sapply(mult_stocks_Spread[,-1], function(x) sum(is.na(x))))
colnames(Missing_Values)<-c( "No_Missing_Values")
# Now we need to convert row names into a column called Tickers
Missing_Values <- data.frame(Tickers = row.names(Missing_Values), Missing_Values)
# Getting ride of row names
rownames(Missing_Values) <- c()
# Now Checking which Rows have missing value.
which(Missing_Values$No_Missing_Values>0)
# Lets see which tickers have missing value.
# Missing_Values[c(195, 292, 446),]
Missing_Values[which(Missing_Values$No_Missing_Values>0),]
```

Now We want to exclude this three stocks from our stock returns.

```{r, include=TRUE}
# Picking those tickers which we want to exclude from out return dataset. 
drops <- Missing_Values[which(Missing_Values$No_Missing_Values>0),]$Tickers
mult_stocks_Spread<-mult_stocks_Spread[ , !(names(mult_stocks_Spread) %in% drops)]
```

We need to transform dataset format into xts. This will help us to calculate Returns.

```{r, include=TRUE}
mult_stocks_Spread.XTS<-xts(mult_stocks_Spread[,-1], order.by = mult_stocks_Spread$Date)
class(mult_stocks_Spread.XTS)
```

For calculating returns, we will use PerformanceAnalytics package. 

```{r, include=TRUE}
# install.packages("PerformanceAnalytics")
library(PerformanceAnalytics)
```

```{r, include=TRUE}
Logarithmic_Returns.XTS<-Return.calculate(mult_stocks_Spread.XTS, method = "log")
head(Logarithmic_Returns.XTS[,1:6])
```



```{r, include=TRUE}
tail(Logarithmic_Returns.XTS[,1:6])
```

```{r, include=TRUE}
Logarithmic_Returns.XTS<-Logarithmic_Returns.XTS[-1,]
head(Logarithmic_Returns.XTS[,1:6])
```


```{r, include=TRUE}
Defensive_Portfolio_Stocks_Logarithmic_Returns.DF<-data.frame(Date=index(Logarithmic_Returns.XTS), coredata(Logarithmic_Returns.XTS))
head(Defensive_Portfolio_Stocks_Logarithmic_Returns.DF[,1:6])
```

```{r, include=TRUE}
write.csv(Defensive_Portfolio_Stocks_Logarithmic_Returns.DF,"C:/Users/Md. Shahadat Hossain/Desktop/Portfolio_Management_2019/Defensive_Portfolio_Stocks_Logarithmic_Returns.csv")
```